### 2012-06-12 trunk/ijcis-pos-model/sources/imperfectionInDB.tex
Forgot something...

%Introductory text:
In this section, some basic concepts are introduced concerning possibilistic variables and fuzzy numbers and intervals, after which the framework of set evaluation by ill-known constraints \cite{Pons2011} is explained. The section concludes with a brief introduction to temporal databases.

@@

\begin{definition}
Consider a universe $U$, $X$ an ill-known value and $CC \triangleq \left \lbrace C_{1_{Z_1}}, \ldots, C_{n_{Z_n}}  \right \rbrace$ a convex combination of ill-known constraints over the variables $Z_1, \ldots, Z_n$. The value $X$ is defined by means of the convex combination:
\begin{align}
\label{eq:ill-known-value-by-convex-constraints}
X \triangleq CC 
\end{align}

The uncertainty about the evaluation of an ill-known value $X$ is given by:
\begin{align}
\label{eq:ill-known-value-def-by-const-unc}
X \in \Pow(U):\pi_{X}=\pi_{CC}
\end{align} 
Note that $\pi_{X}$ is convex since $\pi_{CC}$ is convex as demostrated in theorem \ref{th:convex-combination-ill-known-constraints}.
\end{definition}

\begin{example}
Consider the ill-known values $X = \left[12, 2, 2\right]$ and $Y = \left[18, 2, 1 \right]$. The ill-known value $Z$ is defined using the convex combination $CC$ of constraints $C_1$ and $C_2$:
\begin{align}
\nonumber
CC \triangleq \left \lbrace C_1\left(>,X\right) \wedge C_2(\leq,Y) \right \rbrace \\
\nonumber
Z \triangleq CC
\end{align}
$Z$ is a fuzzy interval defined by a trapezoidal shape given by $\left[12,\ 14,\ 18,\ 19 \right]$
Figure \ref{fig:example-ill-known-by-const} illustrates the relations among the variables $X$, $Y$ and $Z$.
\end{example}

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/ill-known-by-constraints.pdf}
\label{fig:example-ill-known-by-const}
}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{Ill-known values $X$ and $Y$. The grey area represents the ill-known value $Z$ defined by the convex combination of the two ill-known constraints $C_1$ and $C_2$.}
\vspace*{13pt}

>>>>

%Introductory text: explain the problem around uncertainty. General things. Announce what will come.
%Remember: clearly state that everything before this point concerned the crisp case.

%Possibility theory: general things. DO NOT FORGET THE INTERPRETATION PART.

%Possibilistic variables

%Ill-known constraints. Make certain it is clear that entire sets can be evaluated, but we only use intervals...

%Fuzzy numbers and intervals. Give an introduction to make the transition smooth

@@

\begin{definition}
\label{def:convex-combination-ill-known-constraints}
Consider a universe $U$, $X$ an ill-known value and $CC \triangleq \left \lbrace C_{1_{Z_1}}, \ldots, C_{n_{Z_n}}  \right \rbrace$ a convex combination of ill-known constraints over the variables $Z_1, \ldots, Z_n$. The value $X$ is defined by means of the convex combination:
\begin{align}
\label{eq:ill-known-value-by-convex-constraints}
X \triangleq CC 
\end{align}

The uncertainty about the evaluation of an ill-known value $X$ is given by:
\begin{align}
\label{eq:ill-known-value-def-by-const-unc}
X \in \Pow(U):\pi_{X}=\pi_{CC}
\end{align} 
Note that $\pi_{X}$ is convex since $\pi_{CC}$ is convex as demonstrated in theorem \ref{th:convex-combination-ill-known-constraints}.
\end{definition}

\begin{example}
Consider the ill-known values $X = \left[12, 2, 2\right]$ and $Y = \left[18, 2, 1 \right]$. The ill-known value $Z$ is defined using the convex combination $CC$ of constraints $C_1$ and $C_2$:
\begin{align}
\nonumber
CC \triangleq \left \lbrace C_1\left(>,X\right) \wedge C_2(\leq,Y) \right \rbrace \\
\nonumber
Z \triangleq CC
\end{align}
$Z$ is a fuzzy interval defined by a trapezoidal shape given by $\left[12,\ 14,\ 18,\ 19 \right]$.
Figure \ref{fig:example-ill-known-by-const} illustrates the relations among the variables $X$, $Y$ and $Z$.
\end{example}

\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/ill-known-by-constraints.pdf}

}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:example-ill-known-by-const}Ill-known values $X$ and $Y$. The grey area represents the ill-known value $Z$ defined by the convex combination of the two ill-known constraints $C_1$ and $C_2$.}
\vspace*{13pt}
